\section{Message from the Tutorial Co-Chairs}\vspace{2em}
\setheaders%
    {Message from the Tutorial Co-Chairs}%
    {Message from the Tutorial Co-Chairs}
\thispagestyle{emptyheader}

\setlength{\parskip}{1ex}

This section contains the abstracts of the ACL 2017 tutorials. This year we had a joint call-for-tutorials, coordinated with the EACL and EMNLP co-chairs (6 co-chairs in total). We received 26 submissions for the joint ACL/EACL/EMNLP call, and it was a difficult task to make a final selection. The six co-chairs applied the following criteria for evaluation: relevance to ACL community, quality of proposal, quality of instructor, estimate of attendance, relevance of area. The tutorials were then assigned to venues trying to respect proposers' preferences and to balance topics across venues. Nine tutorials had ACL as the preferred conference, from which one was rejected, two were redirected to EMNLP and the rest (six of them) was accepted. All six are organised as half-day tutorials.

We are very grateful to Alex Klementiev and Lucia Specia (EACL tutorial chairs), Nathan Schneider and Alexandra Birch (EMNLP tutorial chairs), Priscilla Rasmussen and Anoop Sarkar (local chairs), Wei Lu, Sameer Singh and Margaret Mitchell (publication chairs), Min-Yen Kan and Regina Barzilay (program co-chairs) and of course Chris Callison-Burch (general chair) for various kinds of help, advice and assistance offered during the process of putting the tutorial programme and materials together. Most importantly, we would like to thank the tutorial presenters for the time and effort in preparing and presenting the tutorials.

We hope you will enjoy the tutorials!

\vskip 0.5in
\noindent ACL 2017 Tutorial Chairs\\
Maja Popović, Humboldt-Universität zu Berlin\\\index{Popović, Maja}
Jordan Boyd-Graber, University of Colorado, Boulder\index{Boyd-Graber, Jordan}
