\begin{bio}
  {\bfseries Xiaodan Zhu} is an Assistant Professor of the Department of Electrical and Computer Engineering of Queen’s University, Canada. Before that, he was a Research Officer of the National Research Council Canada. His research interests are in Natural Language Processing and Machine Learning. His recent work has focused on deep learning, semantic composition, sentiment analysis, and natural language inference.
  \index{Zhu, Xiaodan}

  {\bfseries Edward Grefenstette} is a Staff Research Scientist at DeepMind. His research covers the intersection of Machine Learning, Computer Reasoning, and Natural Language Understanding. Recent publications cover the topics of neural computation, representation learning at the sentence level, recognising textual entailment, and machine reading. 
  \index{Grefenstette, Edward}
\end{bio}

\begin{tutorial}
  {Deep Learning for Semantic Composition}
  {tutorial-003}
  {\daydateyear, \tutorialmorningtime}
  {\TutLocC}

Learning representation to model the meaning of text has been a core problem in NLP. The last several years have seen extensive interests on distributional approaches, in which text spans of different granularities are encoded as vectors of numerical values. If properly learned, such representation has showed to achieve the state-of-the-art performance on a wide range of NLP problems.
 
In this tutorial, we will cover the fundamentals and the state-of-the-art research on neural network-based modeling for semantic composition, which aims to learn distributed representation for different granularities of text, e.g., phrases, sentences, or even documents, from their sub-component meaning representation, e.g., word embedding.
\end{tutorial}
