\vspace{2em}

\section{Message from the General Chair}\vspace{2em}
\setheaders%
    {Message from the General Chair}%
    {Message from the General Chair}
\thispagestyle{emptyheader}

\setlength{\parskip}{1ex}


Welcome to ACL 2017 on Vancouver!  We hope you enjoy the conference and your
stay in Canada.    This is the 55th annual meeting of the Association for Computational Linguistics.  We are anticipating one of the largest ACL conferences ever.  We had a record number of papers submitted to the conference, and a record number of industry partners joining us as sponsors of the conference.   We are on track to be one of the best attended ACL conferences to date.   I hope that this year's conference is intellectually stimulating and that you take home many new ideas and techniques that will help extend your own research.

Each year, the ACL conference is organized by a dedicated team of volunteers.  Please thank this year's organizers for their service to the community when you see them at the conference.  Without these people, this conference would not happen:  Regina Barzilay and Min-Yen Kan (Program Co-Chairs),
Priscilla Rasmussen and Anoop Sarkar (Local Organizing Committee),
Wei Xu and  Jonathan Berant (Workshop Chairs),
Maja Popovi\'c and Jordan Boyd-Graber (Tutorial Chairs)
Wei Lu, Sameer Singh and Margaret Mitchell (Publication Chairs),
Heng Ji and Mohit Bansal (Demonstration Chairs),
Spandana Gella, Allyson Ettinger, and Matthieu Labeau (Student Research Workshop Organizers),
Cecilia Ovesdotter Alm, Mark Dredze, and Marine Carpuat (Faculty Advisors to the Student Research Workshop),
Charley Chan  (Publicity Chair),
Christian Federmann (Conference Handbook Chair), 
Maryam Siahbani (Student Volunteer Coordinator), 
and 
Nitin Madnani (Webmaster and Appmaster).

The organizers have been working for more than a year to put together the conference.  Far more than a year in advance, the  ACL 2017 Coordinating Committee helped to select the venue and to pick the General Chair and the Program Co-Chairs.  This consisted of members from  NAACL and ACL executive boards. Representing NAACL we had Hal Daum\'e III,  Michael White, Joel Tetreault,  and Emily M.\ Bender.  Representing ACL we had  Pushpak Bhattacharyya, Dragomir Radev,   Graeme Hirst, Yejin Choi, and Priscilla Rasmussen.  I would like to extend a personal thanks to Graeme and Priscilla who often serve as the ACL’s institutional memory, and who have helped fill in many details along the way.

I would like to extend a special thanks to our Program Co-Chairs, Regina Barzilay and Min-Yen Kan.  They documented their work creating the program by running a blog.  They used their blog as a platform for engaging the ACL community in many of the decision making processes including soliciting suggestions for the conference’s area chairs and invited speakers. They hosted discussions with Marti Hearst and Joakim Nivre about the value of publishing pre-prints of submitted paper on arXiv and how they relate to double blind reviewing.  They even invited several prominent members of our community to provide last-minute writing advice.  If you weren’t following the blog in the lead-up to the conference, I highly recommend taking a look through it now.  You can find it linked from the ACL 2017 web page.


This year's program looks like it will be excellent!  We owe a huge thank you
to Regina Barzilay and Min-Yen Kan.  They selected this
year's papers from 1,318 submissions with the help of 44 area chairs and more
than 1,200 reviewers. Thanks to Regina, Min, the area chairs, the reviewers
and the authors. Beyond the papers, we have talks by luminaries in the field
of NLP, including ACL President Joakim Nivre, invited speakers Mirella 
Lapata and Noah Smith, and the recipient of this year's Lifetime Achievement
Award.  We also have an excellent set of workshops and tutorials. 
On the tutorial day, there will also be a special workshop on Women and Underrepresented Minorities in Natural Language Processing.    Thank you to
our workshop organizers and tutorial presenters.

This year we are trying to make ACL more family friendly. We are offering
on-site subsidized childcare for the first time ever, plus a space for nursing
or pumping mothers. Our social event is at the aquarium, which promises to be
a family friendly venue. We hope you bring your loved ones with you.


I would like to thank our many sponsors for their generous contributions.  
Our platinum sponsors are 
Alibaba, 
Amazon, 
Apple, 
Baidu, 
Bloomberg, 
Facebook, 
Google, 
Samsung and 
Tencent.  
Our gold sponsors are 
eBay, 
Elsevier, 
IBM Research, 
KPMG, 
Maluuba, 
Microsoft, 
Naver Line, 
NEC,
Recruit Institute of Technology, and 
SAP.  
Our silver sponsors are 
Adobe,
Bosch,
CVTE,
Duolingo,
Huawei,
Nuance,
Oracle, and
Sogou.
Our bronze sponsors are 
Grammarly, 
Toutiao, and 
Yandex.  
Our supporters include 
Newsela 
and four professional master’s degree programs from 
Brandeis, 
Columbia, 
NYU and 
the University of Washington.  
We would like to acknowledge the generous support of the National Science Foundation which has awarded a \$15,000 grant to the ACL Student Research Workshop.
Finally, NVIDIA donated several Titan X GPU cards for us to raffle off during the conference. 

Lastly, I would like to thank everyone else who helped to make this conference a success.  Thank you to our area chairs, our army of reviewers, our workshop organizers, our tutorial presenters, our invited speakers, and our authors.  Best regards to all of you.

Enjoy the conference! I hope that you learn something new that inspires you to
push your own research to new heights.  
Welcome to ACL 2017!  

\vskip 0.5in
\noindent Best Regards,\\
Chris Callison-Burch\\
ACL 2017 General Chair

\index{Callison-Burch, Chris}

%%%
% General Chair remarks from ACL proceedings -- use these?
%%%

%Welcome to ACL 2017 in Vancouver, Canada!  This is the 55th annual meeting of the Association for Computational Linguistics.  A tremendous amount of knowledge has been presented at more than half a century's worth of our conferences.  
%% Min: sounds too negative?
%Hopefully, some of it is still relevant now that deep learning has solved language.   We are anticipating one of the largest ACL conferences ever.  We had a record number of papers submitted to the conference, and a record number of industry partners joining us a sponsors of the conference.   We are on track to be one of the best attended ACL conferences to date.   I hope that this year's conference is intellectually stimulating and that you take home many new ideas and techniques that will help extend your own research.

%Each year, the ACL conference is organized by a dedicated team of volunteers.  Please thank this year's organizers for their service to the community when you see them at the conference.  Without these people, this conference would not happen:  Regina Barzilay and Min-Yen Kan (Program Co-Chairs),
%Priscilla Rasmussen and Anoop Sarkar (Local Organizing Committee),
%Wei Xu and  Jonathan Berant (Workshop Chairs),
%Maja Popovi\'c and Jordan Boyd-Graber (Tutorial Chairs)
%Wei Lu, Sameer Singh and Margaret Mitchell (Publication Chairs),
%Heng Ji and Mohit Bansal (Demonstration Chairs),
%Spandana Gella, Allyson Ettinger, and Matthieu Labeau (Student Research Workshop Organizers),
%Cecilia Ovesdotter Alm, Mark Dredze, and Marine Carpuat (Faculty Advisors to the Student Research Workshop),
%Charley Chan  (Publicity Chair),
%Christian Federmann (Conference Handbook Chair), 
%Maryam Siahbani (Student Volunteer Coordinator), 
%and 
%Nitin Madnani (Webmaster and Appmaster).

%The organizers have been working for more than a year to put together the conference.  Far more than a year in advance, the  ACL 2017 Coordinating Committee helped to select the venue and to pick the General Chair and the Program Co-Chairs.  This consisted of members from  NAACL and ACL executive boards. Representing NAACL we had Hal Daum\'e III,  Michael White, Joel Tetreault,  and Emily Bender.  Representing ACL we had  Pushpak Bhattacharyya, Dragomir Radev,   Graeme Hirst, Yejin Choi, and Priscilla Rasmussen.  I would like to extend a personal thanks to Graeme and Priscilla who often serve as the ACL’s institutional memory, and who have helped fill in many details along the way.

%I would like to extend a special thanks to our Program Co-Chairs, Regina Barzilay and Min-Yen Kan.  They documented their work creating the program by running a blog.  They used their blog as a platform for engaging the ACL community in many of the decision making processes including soliciting suggestions for the conference’s area chairs and invited speakers.
%% Min: ArXiv => 
%arXiv  They hosted discussions with Marti Hearst and Joakim Nivre about the value of publishing pre-prints of submitted paper on arXiv and how they relate to double blind reviewing.  They even invited several prominent members of our community to provide last-minute writing advice.  If you weren’t following the blog in the lead-up to the conference, I highly recommend taking a look through it now.  You can find it linked from the ACL 2017 web page.

%This year’s conference features two outreach activities that I would like to highlight.  First, on Sunday, July 30, 2017, there will be a workshop on Women and Underrepresented Minorities in Natural Language Processing organized by Libby Barak, Isabelle Augenstein, Chlo\'e Braud, He He,  and Margaret Mitchell.  
%% Min: overrepresented amounts of  underrepresentedness.
%The goals of the workshop are to increase awareness of the work women and underrepresented groups do, support women and underrepresented groups in continuing to pursue their research, and  motivate long-term resourcesfor underrepresented groups within ACL.
%Second, for the first time ever, ACL is offering subsidized on-site childcare at the conference hotel.  The goal of this is to allow ACL participants with children to more readily be able to attend the conference. Since childcare duties often fall disproportionately on women, our hope is that by having professional childcare on-site that we will allow more women to participate, and therefore to help promote their careers.  My hope is that the childcare will be successful, and continued in future conferences. 

%I would like to thank our many sponsors for their generous contributions.  
%Our platinum sponsors are 
%Alibaba, 
%Amazon, 
%Apple, 
%Baidu, 
%Bloomberg, 
%Facebook, 
%Google, 
%Samsung and 
%Tencent.  
%Our gold sponsors are 
%eBay, 
%Elsevier, 
%IBM Research, 
%KPMG, 
%Maluuba, 
%Microsoft, 
%Naver Line, 
%Recruit Institute of Technology, and 
%SAP.  
%Our silver sponsors are 
%Adobe,
%Bosch,
%CVTE,
%% Min: I thought this is capitalized from their website? Duolingo?
%duolingo,
%Huawei,
%Nuance,
%Oracle, and
%Sogou.
%Our bronze sponsors are 
%% Min: I thought this is capitalized from their website? Grammarly?
%grammarly, 
%Toutiao, and 
%Yandex.  
%Our supporters include 
%Newsela 
%and four professional master’s degree programs from 
%% Min: spell out? Brandeis University (since you have UoW)?
%Brandeis, 
%Columbia, 
%% Min: Spell out?
%NYU and 
%the University of Washington.  
%We would like to acknowledge the generous support of the National Science Foundation which has awarded a \$15,000 grant to the ACL Student Research Workshop.
%Finally, NVIDIA donated several Titan X GPU cards for us to raffle off during the conference. 

%Lastly, I would like to thank everyone else who helped to make this conference a success.  Thank you to our area chairs, our army of reviewers, our workshop organizers, our tutorial presenters, our invited speakers, and our authors.  Best regards to all of you.

%Welcome to ACL 2017!

%Chris Callison-Burch \\General Chair
