\chapter{Local Guide}

\emph{This guide was written by Anoop Sarkar, with additions by Christian Federmann.}
\index{Sarkar, Anoop}\index{Federmann, Christian}

Vancouver, BC has several events scheduled during the summer time and we would like to highlight some of the events that will be happening either during ACL 2017 or just before or just after the conference. This is also an important reminder to those planning to attend the conference that you should book your hotel room immediately. It is very likely that there will be a shortage of hotel rooms due to the various festivals in the city at around the same time as ACL 2017.

The main festivals happening in the city during ACL 2017 are:

\paragraph{Vancouver Pride Festival}
The Vancouver Pride Festivalthis year will held in downtown Vancouver on Sunday, August 6, 2017. There are more than 20 official events aimed at bringing together the LGBTQ community and their friends, allies and supporters. The main event is the festival parade which will be held in downtown Vancouver within walking distance of the conference hotel. There is more information at the Tourism Vancouver site.
%
\begin{itemize}
\item[--]\url{http://www.vancouverpride.ca/}
\item[--]\url{https://www.tourismvancouver.com/events/festivals-and-events/vancouver-pride-festival/}
\end{itemize}

\paragraph{Celebration of Light}
The Celebration of Light is a competition in which three countries compete to put on the best fireworks display. The fireworks start at 10pm over English Bay in Downtown Vancouver. This year the three countries competing are: Japan on Saturday, July 29th; the UK on Wednesday, August 2nd; and Canada on Saturday, August 5, 2017. Tickets are on sale for venues close to the fireworks display. It is not a long walk to English Bay from the conference hotel and you might be able to catch the fireworks without purchasing a ticket. There is more information at the Tourism Vancouver site.
%
\begin{itemize}
\item[--]\url{http://hondacelebrationoflight.com/}
\item[--]\url{https://www.tourismvancouver.com/events/festivals-and-events/celebration-of-light/}
\end{itemize}

\paragraph{Caribbean Days}
Caribbean Days is a multicultural festival celebrating Caribbean culture which will be held this year in North Vancouver, BC on July 29 and 30, 2017. North Vancouver is a short ferry ride or car/bus ride away from downtown Vancouver. There is more information at the Tourism Vancouver site.
%
\begin{itemize}
\item[--]\url{http://www.caribbeandays.ca/}
\item[--]\url{https://www.tourismvancouver.com/events/festivals-and-events/10-unique-vancouver-festivals/}
\end{itemize}

\paragraph{Vancouver Folk Music Festival}
This event is a bit before the conference dates but is a large event and you might want to catch some of it before the conference begins. The Vancouver Folk Music Festival will be held at Jericho Beach in Vancouver, BC on July 14-16, 2017. There is more information at the Tourism Vancouver site.
%
\begin{itemize}
\item[--]\url{http://thefestival.bc.ca/}
\item[--]\url{https://www.tourismvancouver.com/events/festivals-and-events/vancouver-folk-music-festivals/}
\end{itemize}

\paragraph{Bard on the Beach: Shakespeare Festival}
The Bard on the Beach stages Shakespeare in Vanier Park, Vancouver, BC during the late summer. Plays are held between June 1 to September 23, 2017. More information.
%
\begin{itemize}
\item[--]\url{https://bardonthebeach.org/}
\item[--]\url{https://www.tourismvancouver.com/events/festivals-and-events/bard-on-the-beach-shakespeare-festival/}
\end{itemize}

\paragraph{Theatre under the Stars}
Theatre under the Stars stages Broadway musicals in Stanley Park, Vancouver, BC. Performances are held between July 7 and August 19, 2017. More information.
%
\begin{itemize}
\item[--]\url{https://www.tuts.ca/}
\item[--]\url{https://www.tourismvancouver.com/events/festivals-and-events/theatre-under-the-stars/}
\end{itemize}

\paragraph{Transportation}
The Downtown Vancouver area is pretty well connected with buses and taxis. The city has recently introduced more bike lanes, so biking is also an option to get around. Note that there are no ride sharing solutions in Vancouver as they are illegal in BC.
%
\begin{itemize}
\item[--]\url{http://vancouver.ca/streets-transportation/visitors-guide-to-public-transit.aspx}
\item[--]\url{https://www.translink.ca/}
\end{itemize}

\paragraph{Safety}
Vancouver is a pretty safe city. Parts of East Hastings Street are home to Vancouver's drug scene and can be unsettling at first sight. During day time, there should not be any problems though. In general, you should be aware of your surroundings in the evening, as you would be in any big city. Vancouver's West End and the False Creek areas are relaxed.
